Usage metrics

### 2020-12-04 inst/analysis/usage_metrics.Rmd
Correct median and max for amount of code given to eval.

---
title: "Usage metrics"
author: "Pierre Donat-Bouillud"
output: html_document
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
  base_dir: /var/lib/R/project-evalR
  calls_packages_path: /run/package-evals-traced.7/summarized-externals.fst
  corpus_path: /revalstudy/inst/data/corpus.fst
---

@@

now <- Sys.time() 
library(tidyverse)
library(stringr)
library(fst)
library(fs)

@@

nb_no_calls_to_eval <- nrow(corpus) - nrow(packages_at_least_one_call_site) # corpus seems to be wrong

@@

```{r call-sites-violin-plot}
call_sites_per_package %>%
 ggplot(aes(x = eval_source, y = nb_call_sites, fill = eval_function), na.rm = TRUE) +
  geom_violin(trim = FALSE, width=1.7)+
  geom_boxplot(data = slice_sample(call_sites_per_package, n = 100000), width=.03) + # too slow otherwise
  #scale_y_log10(labels = scales::comma) +
  labs(y="Call sites per package") +
  theme(
    legend.position=c(0.5, 0.85),
    legend.box.background = element_rect(fill="white", size=0.1),
    legend.box="horizontal",
    axis.title.x=element_blank()
  )

#ggsave(path(PLOT_DIR, "call_sites_per_packages.pdf"))
```

@@

```{r eval-calls-violin-plot}
eval_calls_per_package %>%
 ggplot(aes(x = eval_source, y = n), na.rm = TRUE) +
  geom_violin(trim = FALSE, width=1.7)+
  geom_boxplot(data = slice_sample(eval_calls_per_package, n = 100000), width=.03) + # too slow otherwise
  #scale_y_log10(labels = scales::comma) +
  labs(y="Eval calls per package") +
  theme(
    legend.position=c(0.5, 0.85),
    legend.box.background = element_rect(fill="white", size=0.1),
    legend.box="horizontal",
    axis.title.x=element_blank()
  )

@@

```{r}
nb_eval_calls_tot <- eval_calls %>% count(wt = nb_ev_calls)
```

If we don't exclude dependent calls, there are `r nb_eval_calls_tot` eval calls, so the proper eval calls are `r ratio(nb_eval_calls, nb_eval_calls_tot$n)` of the total.

@@

weighted.median <- function(x, w) {
  w <- w[order(x)]
  x <- x[order(x)]

@@

med_size <- own_eval_calls %>% summarise(med = median(expr_expression_length, na.rm = TRUE)) # should be weighted by nb_ev_calls
max_size <- own_eval_calls %>% summarize(m = max(expr_expression_length, na.rm = TRUE))
average_size <- weighted.mean(own_eval_calls$expr_expression_length, na.rm = TRUE, w = own_eval_calls$nb_ev_calls)

@@

```{r nb-events-violin-plot}
own_eval_calls %>%
 ggplot(aes(x = eval_source, y = direct_interpreter_eval), na.rm = TRUE) +
  geom_violin(trim = FALSE, width=1.7)+
  geom_boxplot(data = slice_sample(own_eval_calls, n = 100000), width=.03) + # too slow otherwise
  #scale_y_log10(labels = scales::comma) +
  labs(y="Number of events in eval per package") +
  theme(
    legend.position=c(0.5, 0.85),
    legend.box.background = element_rect(fill="white", size=0.1),
    legend.box="horizontal",
    axis.title.x=element_blank()
  )

>>>>

---
title: "Usage metrics"
author: "Pierre Donat-Bouillud"
output:
    html_document:
        gallery: false
        toc: true
        toc_depth: 3
        toc_float: true
        df_print: paged
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
  base_dir: /var/lib/R/project-evalR
  calls_packages_path: /run/package-evals-traced.9/summarized-externals.fst
  corpus_path: /revalstudy/inst/data/corpus.fst
---

@@

now <- Sys.time() 
library(tidyverse)
library(stringr)
library(fst)
library(fs)
library(DT)

@@

nb_no_calls_to_eval <- nrow(corpus) - n_distinct(select(packages_at_least_one_call_site, eval_source))

@@

```{r call-sites-violin-plot}
call_sites_per_package %>%
 ggplot(aes(x = eval_function, y = nb_call_sites, fill = eval_function), na.rm = TRUE) +
  geom_violin(trim = FALSE, width=1.7)+
  #geom_jitter(shape=16, position=position_jitter(0.2)) +
  labs(y="Call sites per package") +
    theme(
    legend.position=c(0.5, 0.85),
    legend.box.background = element_rect(fill="white", size=0.1),
    legend.box="horizontal",
    axis.title.x=element_blank()
  )

ggsave(path(PLOT_DIR, "call_sites_per_packages.pdf"))
```

@@

```{r eval-calls-violin-plot}
eval_calls_per_package %>%
 ggplot(aes(x = "", y = n, fill = ""), na.rm = TRUE) +
  geom_violin(trim = FALSE, width=1.7)+
  labs(y="Eval calls per package") +
  theme(
    legend.position= "none"
  )

@@

<!-- How is the normalized distribution of eval calls?  -->

<!-- ```{r distribution-call-sites} -->
<!-- eval_calls_per_package %>% -->
<!--   ggplot(aes(x = n), na.rm = TRUE) + -->
<!--   geom_density(adjust = 10) + -->
<!--   scale_y_log10()  -->
<!-- ``` -->

<!-- (Like the violin plot, but smoothed) -->
(th)

@@

weighted.median <- function(x, w, na.rm=FALSE) {
  if(na.rm)
    na.omit(x)
  w <- w[order(x)]
  x <- x[order(x)]

@@

med_size <-  weighted.median(own_eval_calls$expr_expression_length, w = own_eval_calls$nb_ev_calls, na.rm = TRUE)
max_size <- max(own_eval_calls$expr_expression_length, na.rm = TRUE)
average_size <- weighted.mean(own_eval_calls$expr_expression_length, na.rm = TRUE, w = own_eval_calls$nb_ev_calls)

@@

```{r nb-events-violin-plot}
own_eval_calls %>% filter(direct_interpreter_eval > 0) %>%
 ggplot(aes(x = "", y = direct_interpreter_eval, fill = ""), na.rm = TRUE) +
  geom_violin(trim = FALSE, width=1.7)+
  scale_y_log10(labels = scales::comma) +
  labs(y="Number of events in eval per package") +
  theme(
    legend.position="none"
  )
